Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-23 supplement.tex
Suppl section about seed generation

\begin{revision}
  \section{Run times for generating samples}

@@

\begin{figure}
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/stem_weight1-500_mean}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1-500_mean}%
\caption{Comparison of uniform sampling and Boltzmann sampling with
weight $\pi=500$. We show results for two different small structures: (A) single stem structure (B) double stem structure. For each respective structure $R$, we plot the energies $E(S,R)$ of
10000 sampled sequences against the probabilities $Pr(R|S)$ (in log scale). For illustrating the trend, we show moving averages over windows of $\pm 1$ kcal. Note that while only the energy $E(S,R)$ is directly controlled by Boltzmann sampling, this strongly impacts the common negative design objective $Pr(R|S)$.}
\label{fig:negforpos}
\end{figure}

>>>>

\begin{figure}[h!]
\textbf{A}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/stem_weight1-500_mean}%
\textbf{B}~\includegraphicstop[width=0.48\textwidth]{Figs/Plots/doublestem_weight1-500_mean}%
\caption{Comparison of uniform sampling and Boltzmann sampling with
weight $\pi=500$. We show results for two different small structures: (A) single stem structure (B) double stem structure. For each respective structure $R$, we plot the energies $E(S,R)$ of
10000 sampled sequences against the probabilities $Pr(R|S)$ (in log scale). For illustrating the trend, we show moving averages over windows of $\pm 1$ kcal. Note that while only the energy $E(S,R)$ is directly controlled by Boltzmann sampling, this strongly impacts the common negative design objective $Pr(R|S)$.}
\label{fig:negforpos}
\end{figure}

\begin{revision}

  \section{Run times for generating samples}

@@

\section{Effectivity of the seed sequence generation}
\todo[inline]{TODO}

Figure~\ref{fig:seed-generation} shows relative numbers of finished instances and admissible sequences at each iteration of the seed generation procedure for the benchmark set \texttt{3str}. We obtain qualitatively equivalent results for all other benchmark sets (not shown). The top plot illustrates the  precomputation step of our strategy, where weights are calibrated for \GCb\% of 0.6. In this step, we produce sequence of the targeted \GCb\% to determine the linear transformation from the sampling energy model (stacking model) to the Turner model. The bottom plot shows the actual generation of the seed sequences after precomputation. The plot shows that most of the instances are finished after the first iterations, with only a few harder instances that require 2--3 times more iterations. Recall that the seed sequences were designed to have similar energy for all target structures.

\begin{figure}[tbh]
  \centering
  \includegraphics[width=0.7\textwidth]{Figs/SeedGeneration/iterations_gc_3str.pdf}\\
  \includegraphics[width=0.7\textwidth]{Figs/SeedGeneration/iterations_en_3str.pdf}
  \caption{Relative numbers of finished instances and admissible sequences at each iteration of the seed generation procedure for the benchmark set \texttt{3str}.}
  \label{fig:seed-generation}
\end{figure}
